Visualizations for the manuscript

### 2022-01-27 metanalysis_visualization/manuscript_Figures.Rmd
new notebook with potential figures for the manuscript

---
title: "Results visualization across sites"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
editor_options: 
  markdown: 
    wrap: 72
---

## Setting up the R environment

@@

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "tidyr","devtools","RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis", "UpSetR")
paket(listOfPackages)

install_github("jokergoo/ComplexHeatmap")
library( ComplexHeatmap)
```

@@

## Patient Count with Mental Health Related ICD codes

```{r}
thpd_psyCount <- count_icd_all %>%
  pivot_longer(names_to = "counts", cols=c(count_psy, count_icd)) %>%
  mutate( counts = ifelse( counts == "count_psy", "Psy", "Total")) %>%
  ggplot(aes(x = time_p, y = value, fill = counts, color = counts)) +
  facet_grid(siteid~.) +
  geom_point() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(y = "Counts",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Per ", time_period , " patient counts with mental health related ICD codes")) + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=period), colour= "black", size = 0.5)
thpd_psyCount
```

#### Both results together

```{r}
count_icd_all_combined <-  count_icd_all %>%
  group_by(time_p, period) %>% 
  summarise(count_psy_all = sum(count_psy), 
            count_icd_all = sum( count_icd ))

thpd_psyCount_combined <- count_icd_all_combined %>%
  pivot_longer(names_to = "counts", cols=c(count_psy_all, count_icd_all)) %>%
  mutate( counts = ifelse( counts == "count_psy_all", "Psy", "Total")) %>%
  ggplot(aes(x = time_p, y = value, fill = counts, color = counts)) +
  geom_point() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(y = "Counts",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Per ", time_period , " patient counts with mental health related ICD codes")) + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=period), colour= "black", size = 0.5)
thpd_psyCount_combined
```

## Ratio patients with vs without psychiatric conditions
```{r}
ratio_psy_non_psy <- ratios_patients_with_without_psy_all %>%
  ggplot(aes(x = time_p, y = ratio, fill = period, color = period)) +
  geom_point() +
  facet_grid(siteid~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Ratio patient with vs without psychiatric conditions ( per ", time_period,")"))

ratio_psy_non_psy
```

## Percentage: patients with psychiatric conditions / total number of patients

### By site

```{r}
percentage_psy_non_psy <- ratios_patients_with_without_psy_all %>%
  ggplot(aes(x = time_p, y = percentage, color = period)) +
  facet_grid(siteid~.) +
  geom_point() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(y = "Percentage",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage patient with vs total population ( per ", time_period,")")) +
  guides(color = guide_legend(title="Patient diagnoses types"))

percentage_psy_non_psy
```

```{r}
ratios_patients_with_without_psy_all %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=percentage, 
              group = siteid, color = siteid))+
  geom_point( aes(shape=siteid, color=siteid) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Percentage: patients with psychiatric conditions / total number of patients") +
    xlab("period (months)")

ratios_patients_with_without_psy_all %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=ratio, 
              group = siteid, color = siteid))+
    facet_wrap("siteid") +
  geom_point( aes(shape=siteid, color=siteid) ) + 
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Ratio: patients with vs. patients without psychiatric conditions") +
    xlab("period (months)") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8))
```

### By Country

#### Showing each independent site 
```{r}
ratios_patients_with_without_psy_all_country <- left_join( ratios_patients_with_without_psy_all, country_map )
ratios_patients_with_without_psy_all_country %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date )  %>%
  ggplot(aes(x = time_p, y = percentage, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(country~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage: patients with psychiatric conditions / total number of patients ( per ", time_period,")"))
```

#### Aggregating the sites in each country

```{r}
ratios_patients_with_without_psy_all_country <- left_join( ratios_patients_with_without_psy_all, country_map )

ratios_patients_with_without_psy_aggregated <- ratios_patients_with_without_psy_all_country %>%
  group_by( time_p, country ) %>%
  mutate( no_psy = sum( count_no_psy_patients ), 
          psy = sum( count_psy_patients ), 
          total = sum(count_no_psy_patients) + sum(count_psy_patients), 
          ratio_by_country = psy / no_psy, 
          perc_by_country = 100*(psy / total) ) %>%
  select( time_p, no_psy, psy, total, ratio_by_country, perc_by_country, country)

ratios_patients_with_without_psy_aggregated %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=perc_by_country, 
              group = country, color = country))+
  geom_point( aes(shape=country, color=country) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_colour_viridis_d() +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle(paste0("Percentage: patients with psychiatric conditions / total number of patients ( per ", time_period,") \n (aggregated by country)")) +
    xlab("period (months)") +
    ylab("percentage (%)")
```

## Ratio: patients with vs. patients without psychiatric conditions

### By site
```{r}
ratios_patients_with_without_psy_all %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=ratio, 
              group = siteid, color = siteid))+
  geom_point( aes(shape=siteid, color=siteid) ) + 
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Ratio: patients with vs. patients without psychiatric conditions") +
    xlab("period (months)")

@@

### By Country

#### Showing each site per country 
```{r}
ratios_patients_with_without_psy_all_country %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot(aes(x = time_p, y = ratio, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(country~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Ratio patient with vs without psychiatric conditions ( per ", time_period,")"))
```

#### Aggregating the values of the sites per country

```{r}
ratios_patients_with_without_psy_aggregated %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=ratio_by_country, 
              group = country, color = country))+
  geom_point( aes(shape=country, color=country) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_colour_viridis_d() +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Ratios: patients with psychiatric conditions / without psychiatric conditions \n (aggregated by country)") +
    xlab("period (months)") +
    ylab("ratio")
```

## Meta-analysis percentage

```{r, results='hide', fig.show='hide'}
#split this into before and after pandemic and run it twice (one for each subset)

#estimate the summary effect size
ratios_patients_with_without_psy_all$total <- ratios_patients_with_without_psy_all$count_no_psy_patients + ratios_patients_with_without_psy_all$count_psy_patients

ratios_bp <- ratios_patients_with_without_psy_all %>%
  filter( period == "before_pandemic")

ratios_dp <- ratios_patients_with_without_psy_all %>%
  filter( period == "during_pandemic")

metainputdata <- ratios_dp
#RR no transformation
#PLO the logit transformation
#PFT the double arcsine transformation
ies=escalc(xi=count_psy_patients, ni=total, data=metainputdata, measure="PR")
summary(ies$vi)

# pool the individual effect size
# DL random effects using the DerSimonian-Laird estimator
#REML random effects using the restricted maximum-likelihood estimator
pes = rma(yi, vi, data=ies, method="REML")
print(pes)
confint(pes)

pes.summary=metaprop(count_psy_patients, total, as.character(time_p),
                     data=metainputdata, 
                     sm="PRAW")
forest(pes.summary,layout = "JAMA")
```

@@

## Percentage of patients by disorder group

```{r}
perc_disorder_group_all %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date &
           disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" )) %>%
  ggplot(aes(x = time_p, y = percentage_dg, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(. ~ disorder_group) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Percentage of patients (%)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage of patients by disorder group \n ( per ", time_period,")"))

perc_disorder_group_all %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date &
          #disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" )) %>%
          disorder_group %in% c("Suicide or Self-Injury" )) %>%
  ggplot(aes(x = time_p, y = percentage_dg, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Percentage of patients (%)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage of patients with Suicide or Self-Injury \n ( per ", time_period,")"))
```

## Sex ratio per site

```{r}
sex_ratio_by_site <- patients_hospitalized_agg_sex_perc_all %>%
  filter( sex == "female") %>%
  group_by( time_p, siteid ) %>%
  mutate( female_count = count_sex, 
          male_count = count - count_sex, 
          sex_ratio_by_site = female_count / male_count ) %>%
  select( time_p, female_count, male_count, sex_ratio_by_site, siteid)

sex_ratio_by_site %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date) %>%
  ggplot(aes(x = time_p, y = sex_ratio_by_site, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
   geom_hline(yintercept = 1,
             linetype = "dashed", color = "red") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "sex ratio (female/male)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Sex ratio of patients with mental disorders \n ( per ", time_period,")"))
```

### Summary of the codes used per site 
```{r}
mental_codes_qc_output_all <- mental_codes_qc_output_all %>%
    mutate( concept_code = gsub("[.]", "", concept_code ) ) %>%
  unique()

summary_codes <- mental_codes_qc_output_all %>%
  select( disorder_group, description, concept_code, distinct_patients, siteid ) %>%
  spread( siteid, distinct_patients)

## add a column with the sites combination 
getSitesWithEachCode <- function(row) {
  sites <- c( row['BCH'],  row['Lurie'], row['UMICH'], row['FRBDX'], row['CHOP'])
  sites <- sites[!is.na( sites ) ]
  siteVal <- paste0( names( sites ), collapse = " - ")
  return( siteVal)
}
summary_codes <- summary_codes[, c("disorder_group", "description", "concept_code", 
                                   "BCH", "CHOP","Lurie", "UMICH",  "FRBDX") ]                        
summary_codes$sitesCombination <- apply(summary_codes, 1, FUN = getSitesWithEachCode)
summary_codes <- summary_codes[
  with(summary_codes, order(BCH, CHOP, FRBDX, Lurie, UMICH, decreasing = TRUE)),
]
print( paste0("There are in total ", nrow( summary_codes[ summary_codes$sitesCombination == "BCH - CHOP - Lurie - UMICH - FRBDX", ]), " codes in common across all sites"))

write.table( summary_codes, file="summary_codes.txt", col.names = TRUE, row.names = FALSE, sep = "\t", quote = FALSE )

#### upSetR 
upsetForDisorderGroup <- function( df, disorderGroup = "ALL"){
  if( disorderGroup != "ALL"){
     df <- df %>%
       filter( disorder_group == disorderGroup ) 
  }

  BCH_concepts = df[ df$siteid == "BCH", "concept_code"]
  FRBDX_concepts = df[ df$siteid == "FRBDX", "concept_code"]
  Lurie_concepts = df[ df$siteid == "Lurie", "concept_code"]
  UMICH_concepts = df[ df$siteid == "UMICH", "concept_code"]
  CHOP_concepts = df[ df$siteid == "CHOP", "concept_code"]

  concepts = list( 
          BCH = BCH_concepts$concept_code,
          FRBDX = FRBDX_concepts$concept_code, 
          Lurie = Lurie_concepts$concept_code, 
          UMICH = UMICH_concepts$concept_code, 
          CHOP  = CHOP_concepts$concept_code
          )
  output <- upset(fromList(concepts), order.by = "freq")
  return( output )
}

upsetForDisorderGroup( df = mental_codes_qc_output_all, disorderGroup = "ALL")
```

@@

numberOfCodesPerDisorderGroup %>%
  mutate( disorder_group = swr( disorder_group ) ) %>%
  inner_join( country_map ) %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
```

>>>>

---
title: "Visualizations for the manuscript"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "tidyr","devtools","RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis", "UpSetR", "scales")
paket(listOfPackages)

install_github("jokergoo/ComplexHeatmap")
install_github("teunbrand/ggh4x")

library( ComplexHeatmap)
library( ggh4x )
```

@@

### Table 1

```{r}
sitesWithTable1 <- outputFiles[c(1,3:5)]

for( i in 1:length( sitesWithTable1 )){
  print(i)
  load(paste0( outputDir, sitesWithTable1[i]))
  if( i == 1 ){
    table1_all <- table1
  } else {
    table1_all <- rbind( table1_all, table1)
  }
  rm( table1)
}
```

### Sex Summary
```{r}
sexInfo_per_country <- table1_all %>%
  filter( Category == "Sex") %>%
  mutate ( counts_before = as.numeric(sapply(strsplit( as.character(before_pandemic), " "), '[', 1)), 
           counts_during = as.numeric(sapply(strsplit( as.character(during_pandemic), " "), '[', 1))) %>%
  select( name, siteid, counts_before, counts_during ) %>%
  inner_join( country_map ) %>%
  group_by( name, country ) %>%
  summarise( before = sum( counts_before), 
             during = sum( counts_during )) %>%
  pivot_longer(names_to = "period", cols=c(before, during))

sexInfo_all <- table1_all %>%
  filter( Category == "Sex") %>%
  mutate ( counts_before = as.numeric(sapply(strsplit( as.character(before_pandemic), " "), '[', 1)), 
           counts_during = as.numeric(sapply(strsplit( as.character(during_pandemic), " "), '[', 1))) %>%
  select( name, siteid, counts_before, counts_during ) %>%
  inner_join( country_map ) %>%
  group_by( name ) %>%
  summarise( before = sum( counts_before), 
             during = sum( counts_during )) %>%
  pivot_longer(names_to = "period", cols=c(before, during)) %>%
  mutate( country = 'ALL' ) %>%
  select( name, country, period, value ) %>%
  rbind( sexInfo_per_country)

sexInfo_all %>%
  ggplot( aes( x= name, y = value, fill = period )) +
  geom_bar( stat = "identity", position = "dodge") +
  facet_wrap("country", scales = "free_y") + 
  labs(x ="", y = "number of patients") +
  theme(axis.text.x=element_text(hjust=1, size = 8), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))+ 
  scale_fill_manual("Pandemic \n period", values = c("before" = "grey", "during" = "orange"))

@@

```{r}
patients_hospitalized_agg_sex_total <- patients_hospitalized_agg_sex_perc_all %>%
  select( - percentage ) %>%
  group_by( time_p, sex ) %>%
  mutate( total_cases = sum( count ), 
          sex_cases = sum( count_sex ), 
          percentage = 100* sex_cases / total_cases, 
          country = "ALL")

patients_hospitalized_agg_sex_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = sex )) +
  geom_line( aes( linetype = sex , color = sex)) +
  geom_point( aes( shape = sex, color = sex )) +
  scale_colour_manual(values=c("#FF6600","#339999")) +
  scale_fill_manual(values=c("#FF6600","#339999"))+
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

patients_hospitalized_agg_sex_country <- patients_hospitalized_agg_sex_perc_all %>%
  select( - percentage ) %>%
  inner_join( country_map ) %>%
  group_by( time_p, sex, country ) %>%
  mutate( total_cases = sum( count ), 
          sex_cases = sum( count_sex ), 
          percentage = 100* sex_cases / total_cases) %>%
  rbind( patients_hospitalized_agg_sex_total)

patients_hospitalized_agg_sex_country %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = sex )) +
  geom_line( aes(linetype = sex, color = sex )) +
  geom_point( aes( shape= sex, color = sex )) +
  scale_colour_manual(values=c("#FF6600","#339999")) +
  scale_fill_manual(values=c("#FF6600","#339999"))+
  #scale_y_continuous(breaks = seq(0, 30, by = 1)) +
  facet_wrap2("country", axes = "all") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "2 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
```

## Interrupted Time Series Analysis

@@

### Disorder group 
```{r}
perc_disorder_group_total <- perc_disorder_group_all %>%
  select( - percentage_dg ) %>%
  group_by( time_p, disorder_group ) %>%
  mutate( total_cases = sum( count_icd ), 
          dg_cases = sum( count_dg ), 
          percentage = 100* dg_cases / total_cases, 
          country = "ALL")

perc_disorder_group_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

perc_disorder_group_country <- perc_disorder_group_all %>%
  select( - percentage_dg ) %>%
  inner_join( country_map ) %>%
  group_by( time_p, disorder_group, country ) %>%
  mutate( total_cases = sum( count_icd ), 
          dg_cases = sum( count_dg ), 
          percentage = 100* dg_cases / total_cases ) %>%
  rbind( perc_disorder_group_total)

perc_disorder_group_country %>%
  filter( disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury", 
  "Mental Health Symptoms", "Obsessive-Compulsive and Related Disorders" )) %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  geom_line( aes(linetype = disorder_group, color = disorder_group )) +
  geom_point( aes( shape= disorder_group, color = disorder_group )) +
  scale_y_continuous(breaks = seq(0, 30, by = 1)) +
  facet_wrap2("country", axes = "all") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "2 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

perc_disorder_group_country %>%
  filter( disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury", 
  "Mental Health Symptoms", "Obsessive-Compulsive and Related Disorders" )) %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  geom_line( aes(linetype = country, color = country )) +
  geom_point( aes( shape= country, color = country )) +
  scale_y_continuous(breaks = seq(0, 30, by = 5)) +
  facet_wrap2("disorder_group", axes = "all") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "2 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

@@

numberOfCodesPerDisorderGroup %>%
  mutate( disorder_group = swr( disorder_group ) ) %>%
  inner_join( country_map ) %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
```
